Testing the Evolution of the Correlations between Supermassive Black Holes and their Host Galaxies using Eight Strongly Lensed quasars

### 2020-05-22 manuscript/manuscript.tex
Update manuscript.tex
Update paper

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[X. Ding et al.]{
Xuheng Ding$^{1}$\thanks{E-mail: dxh@astro.ucla.edu},
Tommaso Treu$^{1}$,
Simon Birrer$^{2}$,
Adriano Agnello$^{3}$,\newauthor
Dominique Sluse$^{4}$,
Chris Fassnacht$^{5}$,
Matthew W. Auger$^{6}$,
Kenneth C. Wong$^{7}$, \newauthor
Sherry H. Suyu$^{8,9,10}$,
Takahiro Morshita$^{11}$,
Aymeric Galan$^{12}$,
and et al.
\\
\\
\\
% List of institutions
$^{1}$Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-1547, USA\\
$^{2}$Kavli Institute for Particle Astrophysics and Cosmology and Department of Physics, Stanford University, Stanford, CA 94305, USA\\
$^{3}$European Southern Observatory, Karl-Schwarzschild-Strasse 2, 85748 Garching, Germany\\
$^{4}$STAR Institute, Quartier Agora - All\'ee du six Ao\^ut, 19c B-4000 Li\`ege, Belgium\\
$^{5}$Department of Physics, University of California, Davis, CA 95616, USA\\
$^{6}$Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK\\
$^{7}$Kavli IPMU (WPI), UTIAS, The University of Tokyo, Kashiwa, Chiba 277-8583, Japan\\
$^{8}$Max-Planck-Institut f{\"u}r Astrophysik, Karl-Schwarzschild-Str.~1, 85748 Garching, Germany\\
$^{9}$Physik-Department, Technische Universit\"at M\"unchen, James-Franck-Stra\ss{}e~1, 85748 Garching, Germany\\
$^{10}$Academia Sinica Institute of Astronomy and Astrophysics (ASIAA), 11F of ASMAB, No.1, Section 4, Roosevelt Road, Taipei 10617, Taiwan\\
$^{11}$Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218, USA\\
$^{12}$Institute of Physics, Laboratory of Astrophysics, Ecole Polytechnique 
F\'ed\'erale de Lausanne (EPFL), Observatoire de Sauverny, 1290 Versoix, 
Switzerland\\
$^{13}$TBC
}

@@

This paper is structured as follows. In Section~\ref{sec:sample_select}, we introduce the sample including their imaging data and the BH masses. In Section~\ref{sec:lens_model}, we describe our approach designed to infer the lens models and reconstruct the host galaxy. We use the inferred photometry to derive the stellar mass and the scaling relations and combine with D20 sample to study the evolution in Section~\ref{sec:result}. Discussion and conclusions are drawn in Section~\ref{sec:diss} and~\ref{sec:con}. Throughout this paper, we adopt a standard concordance cosmology with parameters adopted as $H_0= 70$ km s$^{-1}$ Mpc$^{-1}$, $\Omega{_m} = 0.30$, and $\Omega{_\Lambda} = 0.70$, \pink{to compute the luminosity distance and estimate the host absolute brightness}. Magnitudes are presented in the AB system. A Chabrier initial mass function (IMF) is employed for the sample, to be consistent with D20.

\section{Sample Selection and Black Hole Mass Estimates}\label{sec:sample_select}
We adopt eight lens systems from our H0LiCOW collaboration including HE0435$-$1223, RXJ1131$-$1231, WFI2033$-$4723, HE1104$-$1805, SDSS1206$+$4332, SDSS0246$-$0825, HE0047$-$1756 and HS2209$+$1914. We refer to~\citet{Suyu2017, Ding2017a} for the descriptions of these data. We summarize the information for the eight systems, including their redshift and data conditions in Table~\ref{data_set}.
For conciseness, in the rest of this paper, we abbreviate each lens name to four digits (e.g., HE0435$-$1223 to HE0435).

Based on the observational data of these eight systems, \citet{Ding2017a} performed an extensive and realistic simulation exercise using the \hst\ image data and confirmed that the source reconstruction using the lens modelling technique is trustworthy. Here, we re-summarize the imaging data information and list them in Table~\ref{data_set}. Besides the imaging data shown in this table, we also analyzed the multi-band \hst\ imaging data to derive the host color information for 3/8 systems. As we show in Section~\ref{sec:mstar}, we use the color information to fit for the best stellar population to improve the accuracy of the estimate of \mstar.

@@

\begin{table*}
\centering
%\begin{threeparttable}
\caption{Summary of lensed AGN observational details.}\label{data_set}
\resizebox{15cm}{!}{
     \begin{tabular}{ccccccccc}
        \hline
Object ID & $z$ & camera & Filter & exposure & Program ID & PI & pixel scale & References \\
 & & & & time (s) &&& (drizzled) & \\ \hline
HE0435$-$1223 & 1.69 & WFC3-IR & F160W & 9340 & 12889 & S. H. Suyu & $0\farcs{}08$ & (1), (2)\\
RXJ1131$-$1231 & 0.65 & ACS & F814W & 1980 & 9744 & C.S. Kochanek & $0\farcs{}05$ &(3), (4)\\
WFI2033$-$4723 & 1.66 & WFC3-IR & F160W & 26257 & 12889 & S. H. Suyu & $0\farcs{}08$ & (5), (2) \\
SDSS1206$+$4332 & 1.79 & WFC3-IR & F160W & 8457 & 14254 & T. Treu & $0\farcs{}08$ & (6), (7)\\
HE1104$-$1805 & 2.32 & WFC3-IR & F160W & 14698 & 12889 & S. H. Suyu  & $0\farcs{}08$ & (8), (9)\\
SDSS0246$-$0825 & 1.68 & WFC3-UVIS & F814W & 8481 & 14254 & T. Treu & $0\farcs{}03$& (10), (11) \\
HS2209$+$1914$^a$  & 1.07 & WFC3-UVIS & F814W & 9696 + 4542 & 14254 & T. Treu & $0\farcs{}03$ & (12), (13) \\
HE0047$-$1756 & 1.66 & WFC3-UVIS & F814W & 9712 & 14254 & T. Treu & $0\farcs{}03$ & (14), (15) \\
        \hline
     \end{tabular}
    }
\begin{tablenotes}
      \small
      \item Note: $-$ The observational information is also given by~\citet{Ding2017a}.
      \item $^a$: HS2209, was visited by \hst\ twice ({\it vis05} and {\it vis06}) at different orientations. The exposure time is thus given separately.
      \item References:$-$ (1) \citet{HE0435_discover}; (2) \citet{Sluse2012}; (3) \citet{1131_discover}; (4) \citet{1131_redshift}; (5) \citet{2033_discover}; (6) \citet{1206_discover}; (7) \citet{Eul++13}; (8) \citet{HE1104_discover}; (9) \citet{1104_d_redshift}; (10) \citet{0246_discover}; (11) \citet{0246_redshift}; (12) \citet{2209_discover};  (13) \citet{2209_more}; (14) \citet{0047_discover}; (15) \citet{Ofe++06};

@@

To ensure the consistency of \mbh\ estimates based on different broad lines, we adopt the following set of self-consistent recipes following D20:
\begin{eqnarray}
\label{recipe}
\log \left(\frac{\mathcal M_{\rm BH}}{M_{\odot}}\right)&~=~& a+b \log \left(\frac{ \rm L _{\lambda_{line}}}{10^{44}{\rm erg~s^{-1}}}\right) \nonumber\\
&~+~& 2 \log \left(\frac{\rm FWHM(line)}{1000 ~{\rm km~s^{-1}}}\right) , 
\end {eqnarray}
\pink{where $\lambda_{\rm line}$ is the reference wavelength of the local continuum luminosities for different emission lines. The following values are adopted:}
%
$a$\{\Civ, \Mgii, \Hb\}=\{6.322, 6.623, 6.910\},
$b$\{\Civ, \Mgii, \Hb\}=\{0.53, 0.47, 0.50\},
$\lambda_{\rm line}$\{\Civ, \Mgii, \Hb\}=\{1350, 3000, 5100\}.
%
The broad line properties of our samples are adopted from the literature, with a few corrections/exceptions. % \citep{Sluse2012, Peng2006, Shen2011}.
The line properties of SDSS1206 have been inferred by~\citet{Shen2011}. However, this system was investigated as a non-lensed AGN and the lensing magnification on the intrinsic continuum luminosity was not considered. We follow~\citet{Birrer2019} and apply the same magnification correction on the $\log(L_\lambda)$ in this work. For the rest of the lens sample except HS2209, their broad line properties are adopted from the literature~\citep{Sluse2012, Peng2006} taking into account lensing magnification. For HS2209, the spectrum was observed at the Keck-II Telescope in September 2015. We derived the line properties from the spectrum using the same approach as~\citet{Sluse2012}, \pink{based on \Mgii}. \todo{Dominique and Chris can give more details here.} . The \mbh\ measurements, together with the properties of the board-line, are listed in Table~\ref{mbh}. 
The uncertainty of the \mbh\ are estimated to be $0.4$~dex.

@@

We follow the standard procedure as described by D20 to prepare the fitting ingredients including the lensing imaging data, noise level map and the PSF information. The imaging data are first drizzled to a higher resolution with a Gaussian kernel; the adopted resolutions are listed in Table~\ref{data_set}. We then adopt the {\sc Photutils}~\citep{photutils} Python package to model the global background light in 2-D, based on the \texttt{SExtractor} algorithm. We remove the background light and cut the clear image data into postage stamp at a suitable size. We draw \pink{an aperture of mask} for each system to define the region in which the pixels will be used to calculate the likelihood; see the top-left panel in each subplot in Figure~\ref{fig:image_inference}.

@@

We employ the imaging modelling tool \lenstronomy\footnote{\url{https://github.com/sibirrer/lenstronomy}}~\citep{lenstronomy} to perform the fitting task. Inspired by D20, we adopt a set of extensive modelling choices to perform the fitting \pink{for each system, repeatedly. Then, based on the fittings using different choices,} we apply a statistical measurement and perform a weighting algorithm to derive the final inference and estimate the uncertainty \pink{level}. The modelling choices that we consider include the follows.
\begin{enumerate}
\item Following common practice, we select all the bright, isolated stars across the image frame of targets to define the PSF. Each selected star is considered as an initial PSF guess for the fit.
\item The central pixels of the AGNs are very bright and can be affected by large systematic errors during the interpolation of the subsampled PSF. To avoid overfitting the noise, we adopt two different modelling options: 1)~manually boost the noise estimate in the central area to effectively infinite ({\it noise boost}); 2)~perform the iterative PSF estimation as introduced by~\citet{Chen2016, Birrer2019} ({\it PSF iteration}).
\item To calculate the ray tracing under a higher resolution grid, we chose to oversample the model by a factor  $2\times2$ or $3\times3$ pixel$^{-1}$.
\item Using the lensing imaging alone, it is difficult to constrain the power-law slope, \pink{especially the model of our host surface brightness is much simplified}. To mitigate the overfitting of the slope value, we repeat the fit for three values $[1.9, 2.0, 2.1]$ that are meant to bracket the range observed in lens galaxies \citep[e.g.,][]{Auger2010}.
\end{enumerate}

In general, for one lens system with a number of $N$ initial PSF guesses, we perform in total $N\times12$ (i.e., $2$ modelling options $\times~2$ oversampling $\times~3$ slopes) fits. After all fits are completed, we rank their performance based on their best-fitted $\chi^2$ value. Since there is no evidence of a better performance for the options between {\it noise boost} and {\it PSF iteration}, we selected the top-4 fittings from each of them and then combine their best-fit results based on the weighting algorithm introduced by D20. The weights are defined by:
\begin{eqnarray}
\label{eq:weights}
w_i = {\rm exp} \big(- \alpha \frac{ (\chi_i ^2 - \chi_{best} ^2 )}{2 \chi_{best} ^2} \big),
\end{eqnarray} 
where the $\alpha$ is an inflation parameter\footnote{Defining $\alpha$ as the {\it inflation} parameter it is assumed that it is larger than ~$1$, so as to err on the side of caution and include more choices that would be allowed strictly by statistical noise considerations.} so that when $i=4$:
\begin{eqnarray}
\label{eq:alpha}
\alpha \frac{ \chi_{i=4} ^2 - \chi_{best} ^2 }{2 \chi_{best} ^2} = 2.
\end{eqnarray} 
Then, the results for {\it noise boost} and {\it PSF iteration} are combined equally to derive the value of host properties and the root-mean-square error (i.e., $\sigma$ level) based on the weights of the $4+4$ (i.e., {\it noise boost} and {\it PSF iteration}) options by:
\begin{eqnarray}
\label{eq:infer_value}
\bar{x}  =  \frac{  \sum_{i=1}^{N}   x_i * w_i  }{\Sigma w_i} ,
\end{eqnarray} 
\begin{eqnarray}
\label{eq:infer_scatter}
\sigma =   \sqrt{ \frac{  \sum_{i=1}^{N}   (x_i -  \bar{x} ) ^2 * w_i  }{\Sigma w_i} }.
\end{eqnarray}

Our approach uses the relative goodness of fit and ensures that at least 8 sets of best fits are used to estimate the range of systematic uncertainties.

@@

The inference by the best-fit lens model for HE0435 is shown in Figure~\ref{fig:image_inference}-(a). Not surprisingly, we note that the residuals level in the normalized plot appears to be larger than the ones presented by~\citet{Wong2017}. This is primarily due to the fact that the surface brightness of the host galaxy in our model is defined as a \sersic\ profile, which is relatively simple and smooth compared to the pixellated reconstruction technique adopted by {\sc Glee}~\citep{Suy++06, Halk2008, S+H10} or the shapelet technique adopted by \lenstronomy~\citep{Birrer2015}. The smooth features of \sersic\ profile can not capture the clumps in the host galaxy, such as the star-forming regions. Nevertheless, our approach is sufficient to derive a self-consistent one-step inference of the global host light in terms of the \sersic\ flux, i.e. the quantity commonly measured in the literature for non-lensed samples.

@@

\pink{It is worth noting that the HE1104 has been modelled by~\citet{Peng2006} based on the \hst/NICMOS H-band (F160W) imaging data. Their inferred host magnitude is $20.14\pm0.3$ in Vega system, which is also consistent to our inference ($20.00\pm0.15$ in Vega).}
%zeropoint 25.9463(AB) - 24.6949(Vega) = 1.2514
%HE1104 mag:  21.25 (AB)  --> 20.00 (Vega)

@@

\begin{figure*}
\centering
\begin{tabular}{c c}
\subfloat[HE0435]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/HE0435_inference.png}}&
\subfloat[RXJ1131]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/RXJ1131_inference.png}}\\
\subfloat[WFI2033]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/WFI2033_inference.png}}&
\subfloat[SDSS1206]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/SDSS1206_inference.png}}\\
\subfloat[HE1104]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/HE1104_inference.png}}&
\subfloat[SDSS0246]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/SDSS0246_inference.png}}\\
\subfloat[HS2209]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/HS2209_inference.png}}&
\subfloat[HE0047]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/HE0047_inference.png}}\\
\end{tabular}
\caption{\label{fig:image_inference} 
Illustrations of the inference using the best-fit lens model for each system using the AGN center noise level boosted approach. For each figure, the panels from left to right are the follows: Top row: (left to right): (1) observed data, (2) best-fit model (3) residuals divided by the uncertainty level; Bottom row: (left to right): (4) data minus the model PSF and deflector  (i.e., pure lensed arc image), (5) the model of the lensed arc, (6) reconstructed host galaxy in the source plane with caustic line drawn as yellow line. Across all the systems, the lensed arc \pink{feature} can be clearly seen in the \pink{fourth} panel, indicating strong evidence of a detection. In panel (3) and (4), we use white regions to indicate the area where the noise level is boosted. 
}
\end{figure*}

>>>>

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[X. Ding et al.]{
Xuheng Ding,$^{1}$\thanks{E-mail: dxh@astro.ucla.edu}
Tommaso Treu,$^{1}$
Simon Birrer,$^{2}$
Adriano Agnello,$^{3}$\newauthor
Dominique Sluse,$^{4}$
Chris Fassnacht,$^{5}$
Matthew W. Auger,$^{6}$
Kenneth C. Wong,$^{7}$ \newauthor
Sherry H. Suyu,$^{8,9,10}$
Takahiro Morishita,$^{11}$
\pink{
Cristian E. Rusu,$^{12,13,14}$
Aymeric Galan,$^{15}$}\newauthor
and et al.
\\
\\
\\
% List of institutions
$^{1}$Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-1547, USA\\
$^{2}$Kavli Institute for Particle Astrophysics and Cosmology and Department of Physics, Stanford University, Stanford, CA 94305, USA\\
$^{3}$European Southern Observatory, Karl-Schwarzschild-Strasse 2, 85748 Garching, Germany\\
$^{4}$STAR Institute, Quartier Agora - All\'ee du six Ao\^ut, 19c B-4000 Li\`ege, Belgium\\
$^{5}$Department of Physics, University of California, Davis, CA 95616, USA\\
$^{6}$Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK\\
$^{7}$Kavli IPMU (WPI), UTIAS, The University of Tokyo, Kashiwa, Chiba 277-8583, Japan\\
$^{8}$Max-Planck-Institut f{\"u}r Astrophysik, Karl-Schwarzschild-Str.~1, 85748 Garching, Germany\\
$^{9}$Physik-Department, Technische Universit\"at M\"unchen, James-Franck-Stra\ss{}e~1, 85748 Garching, Germany\\
$^{10}$Academia Sinica Institute of Astronomy and Astrophysics (ASIAA), 11F of ASMAB, No.1, Section 4, Roosevelt Road, Taipei 10617, Taiwan\\
$^{11}$Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218, USA\\
$^{12}$National Astronomical Observatory of Japan, 2-21-1 Osawa, Mitaka, Tokyo 181-8588, Japan\\
$^{13}$Subaru Telescope, National Astronomical Observatory of Japan, 650 N Aohoku Pl, Hilo, HI 96720\\
$^{14}$Department of Physics, University of California, Davis, 1 Shields Avenue, Davis, CA 95616, USA\\
$^{15}$Institute of Physics, Laboratory of Astrophysics, Ecole Polytechnique 
F\'ed\'erale de Lausanne (EPFL), Observatoire de Sauverny, 1290 Versoix, 
Switzerland\\
$^{13}$TBC
}

@@

This paper is structured as follows. In Section~\ref{sec:sample_select}, we introduce the sample including their imaging data and the BH masses. In Section~\ref{sec:lens_model}, we describe our approach designed to infer the lens models and reconstruct the host galaxy. We use the inferred photometry to derive the stellar mass and the scaling relations and combine with D20 sample to study the evolution in Section~\ref{sec:result}. Discussion and conclusions are drawn in Sections~\ref{sec:diss} and~\ref{sec:con}. Throughout this paper, we adopt a standard concordance cosmology with parameters adopted as $H_0= 70$ km s$^{-1}$ Mpc$^{-1}$, $\Omega{_m} = 0.30$, and $\Omega{_\Lambda} = 0.70$, \pink{to compute the luminosity distance and estimate the host absolute brightness}. Magnitudes are presented in the AB system. A Chabrier initial mass function (IMF) is employed for the sample, to be consistent with D20.

\section{Sample Selection and Black Hole Mass Estimates}\label{sec:sample_select}
We adopt eight lens systems from the H0LiCOW collaboration including HE0435$-$1223, RXJ1131$-$1231, WFI2033$-$4723, HE1104$-$1805, SDSS1206$+$4332, SDSS0246$-$0825, HE0047$-$1756 and HS2209$+$1914. We refer to~\citet{Suyu2017, Ding2017a} for the descriptions of these data. For conciseness, in the rest of this paper, we abbreviate each lens name to four digits (e.g., HE0435$-$1223 to HE0435).

Based on the observational data of these eight systems, \citet{Ding2017a} performed an extensive and realistic simulation exercise using the \hst\ image data and confirmed that the source reconstruction using the lens modelling technique is trustworthy. We summarize the information for the eight systems, including \pink{their redshift, data conditions and the references} in Table~\ref{data_set}.
Besides the imaging data shown in this table, we also analyzed the multi-band \hst\ imaging data to derive the host color information for 3/8 systems. As we show in Section~\ref{sec:mstar}, we use the color information to fit for the best stellar population to improve the accuracy of the estimate of \mstar.

@@

\begin{table*}
\centering
%\begin{threeparttable}
\caption{Summary of lensed AGN observational details.}\label{data_set}
\resizebox{15cm}{!}{
     \begin{tabular}{ccccccccc}
        \hline
Object ID & $z_s$ & camera & Filter & exposure & Program ID & PI & pixel scale & References \\
 & & & & time (s) &&& (drizzled) & \\ \hline
HE0435$-$1223 & 1.69 & WFC3-IR & F160W & 9340 & 12889 & S. H. Suyu & $0\farcs{}08$ & (1), (2)\\
RXJ1131$-$1231 & 0.65 & ACS & F814W & 1980 & 9744 & C.S. Kochanek & $0\farcs{}05$ &(3), (4)\\
WFI2033$-$4723 & 1.66 & WFC3-IR & F160W & 26257 & 12889 & S. H. Suyu & $0\farcs{}08$ & (5), (2) \\
SDSS1206$+$4332 & 1.79 & WFC3-IR & F160W & 8457 & 14254 & T. Treu & $0\farcs{}08$ & (6), (7)\\
HE1104$-$1805 & 2.32 & WFC3-IR & F160W & 14698 & 12889 & S. H. Suyu  & $0\farcs{}08$ & (8), (9)\\
SDSS0246$-$0825 & 1.68 & WFC3-UVIS & F814W & 8481 & 14254 & T. Treu & $0\farcs{}03$& (10), (11) \\
HS2209$+$1914$^a$  & 1.07 & WFC3-UVIS & F814W & 9696 + 4542 & 14254 & T. Treu & $0\farcs{}03$ & (12), (13) \\
HE0047$-$1756 & 1.66 & WFC3-UVIS & F814W & 9712 & 14254 & T. Treu & $0\farcs{}03$ & (14), (15) \\
        \hline
     \end{tabular}
    }
\begin{tablenotes}
      \small
      \item Note: $-$ The observational information is also given by~\citet{Ding2017a}.
      \item $^a$: HS2209, was visited by \hst\ twice ({\it vis05} and {\it vis06}) at different orientations. The exposure time is thus given separately.
      \item References:$-$ (1) \citet{HE0435_discover}; (2) \citet{Sluse2012}; (3) \citet{1131_discover}; (4) \citet{1131_redshift}; (5) \citet{2033_discover}; (6) \citet{1206_discover}; (7) \citet{Eul++13}; (8) \citet{HE1104_discover}; (9) \citet{1104_d_redshift}; (10) \citet{0246_discover}; (11) \citet{0246_redshift}; (12) \citet{2209_discover};  (13) \citet{2209_more}; (14) \citet{0047_discover}; (15) \citet{Ofe++06};

@@

To ensure the consistency of \mbh\ estimates based on different broad lines, we adopt the following set of self-consistent recipes following D20:
\begin{eqnarray}
\label{recipe}
\log \left(\frac{\mathcal M_{\rm BH}}{M_{\odot}}\right)&~=~& a+b \log \left(\frac{ \rm L _{\lambda_{line}}}{10^{44}{\rm erg~s^{-1}}}\right) \nonumber\\
&~+~& 2 \log \left(\frac{\rm FWHM(line)}{1000 ~{\rm km~s^{-1}}}\right) , 
\end {eqnarray}
\pink{where $\lambda_{\rm line}$ is the reference wavelength of the local continuum luminosities for different emission lines. The following values are adopted:}
%
$a$\{\Civ, \Mgii, \Hb\}=\{6.322, 6.623, 6.910\},
$b$\{\Civ, \Mgii, \Hb\}=\{0.53, 0.47, 0.50\},
$\lambda_{\rm line}$\{\Civ, \Mgii, \Hb\}=\{1350, 3000, 5100\} ($\AA$).
%
The broad line properties of our samples are adopted from the literature, with a few corrections/exceptions. % \citep{Sluse2012, Peng2006, Shen2011}.
The line properties of SDSS1206 have been inferred by~\citet{Shen2011}. However, this system was investigated as a non-lensed AGN and the lensing magnification on the intrinsic continuum luminosity was not considered. We follow~\citet{Birrer2019} and apply the same magnification correction on the $\log(L_\lambda)$ in this work. For the rest of the lens sample except HS2209, their broad line properties are adopted from the literature~\citep{Sluse2012, Peng2006} taking into account lensing magnification. For HS2209, the spectrum was observed at the Keck-II Telescope in September 2015. We derived the line properties from the spectrum using the same approach as~\citet{Sluse2012}, \pink{based on \Mgii}. The \mbh\ measurements, together with the properties of the board-line, are listed in Table~\ref{mbh}. 
The uncertainty of the \mbh\ are estimated to be $0.4$~dex.

@@

We follow the standard procedure as described by D20 to prepare the fitting ingredients including the lensing imaging data, noise level map and the PSF information. The imaging data are first drizzled to a higher resolution with a Gaussian kernel; the adopted resolutions are listed in Table~\ref{data_set}. We then adopt the {\sc Photutils}~\citep{photutils} Python package to model the global background light in 2-D, based on the \texttt{SExtractor} algorithm. We remove the background light and cut the clear image data into postage stamp at a suitable size. We draw the image mask for each system to define the region in which the pixels will be used to calculate the likelihood; see the top-\pink{middle} panel in each subplot in Figure~\ref{fig:image_inference}.

@@

We employ the imaging modelling tool \lenstronomy\footnote{\url{https://github.com/sibirrer/lenstronomy}}~\citep{lenstronomy} to perform the fitting task. Inspired by D20, we adopt a set of extensive modelling choices to perform the fitting \pink{for each system, repeatedly. Then, based on the fittings using different choices,} we apply a statistical measurement and perform a weighting algorithm to derive the final inference and estimate the uncertainty \pink{level}. The modelling choices that we consider include the follows.
\begin{enumerate}
\item Following common practice, we select all the bright, isolated stars across the image frame of targets to define the PSF. Each selected star is considered as an initial PSF guess for the fit.
\item The central pixels of the AGNs are very bright and can be affected by large systematic errors during the interpolation of the subsampled PSF. To avoid overfitting the noise, we adopt two different modelling options: 1)~manually boost the noise estimate in the central area to effectively infinite ({\it noise boost}); 2)~perform the iterative PSF estimation as introduced by~\citet{Chen2016, Birrer2019} ({\it PSF iteration}).
\item To calculate the ray tracing under a higher resolution grid, we choose to oversample the model by a factor  $2\times2$ or $3\times3$ pixel$^{-1}$.
\item Using the lensing imaging alone, it is difficult to constrain the power-law slope, \pink{especially the model of our host surface brightness is much simplified}. To mitigate the overfitting of the slope value, we repeat the fit for three values $[1.9, 2.0, 2.1]$ that are meant to bracket the range observed in lens galaxies \citep[e.g.,][]{Auger2010}.
\end{enumerate}

In general, for one lens system with a number of $N$ initial PSF guesses, we perform in total $N\times12$ \pink{(i.e., $2$ by (ii) $\times~2$ by (iii) $\times~3$ by (iv)) fits}. After all fits are completed, we rank their performance based on their best-fitted $\chi^2$ value. Since there is no evidence of a better performance for the options between {\it noise boost} and {\it PSF iteration}, we selected the top-4 fittings from each of them and then combine their best-fit results based on the weighting algorithm introduced by D20. The weights are defined by:
\begin{eqnarray}
\label{eq:weights}
w_i = {\rm exp} \big(- \alpha \frac{ (\chi_i ^2 - \chi_{best} ^2 )}{2 \chi_{best} ^2} \big),
\end{eqnarray} 
where the $\alpha$ is an inflation parameter\footnote{Defining $\alpha$ as the {\it inflation} parameter it is assumed that it is larger than ~$1$, so as to err on the side of caution and include more choices that would be allowed strictly by statistical noise considerations.} so that when $i=4$:
\begin{eqnarray}
\label{eq:alpha}
\alpha \frac{ \chi_{i=4} ^2 - \chi_{best} ^2 }{2 \chi_{best} ^2} = 2.
\end{eqnarray} 
Then, the results for {\it noise boost} and {\it PSF iteration} are combined equally to derive the value of host properties and the root-mean-square error (i.e., $\sigma$ level) based on the weights of the $4+4$ (i.e., {\it noise boost} and {\it PSF iteration}) options by:
\begin{eqnarray}
\label{eq:infer_value}
\bar{x}  =  \frac{  \sum_{i=1}^{N}   x_i * w_i  }{\Sigma w_i} ,
\end{eqnarray} 
\begin{eqnarray}
\label{eq:infer_scatter}
\sigma =   \sqrt{ \frac{  \sum_{i=1}^{N}   (x_i -  \bar{x} ) ^2 * w_i  }{\Sigma w_i} }.
\end{eqnarray}

Our approach uses the relative goodness of fit and ensures that at least 8 sets of best fits are used to estimate the range of systematic uncertainties. \pink{Note that the lens mass slope is fixed in each fitting, and the statistical uncertainty is much smaller than the systematic one.}

@@

The inference by the best-fit lens model for HE0435 is shown in Figure~\ref{fig:image_inference}-(a). Not surprisingly, we note that the residuals level in the normalized plot appears to be larger than the ones presented by~\citet{Wong2017}. This is primarily due to the fact that the surface brightness of the host galaxy in our model is defined as a \sersic\ profile, which is relatively simple and smooth compared to the pixellated reconstruction technique adopted by {\sc Glee}~\citep{Suy++06, Halk2008, S+H10, Suyu2012} or the shapelet technique adopted by \lenstronomy~\citep{Birrer2015}. The smooth features of \sersic\ profile can not capture the clumps in the host galaxy, such as the star-forming regions. Nevertheless, our approach is sufficient to derive a self-consistent one-step inference of the global host light in terms of the \sersic\ flux, i.e. the quantity commonly measured in the literature for non-lensed samples.

@@

\pink{It is worth noting that the HE1104 has been modelled by~\citet{Peng2006} based on the \hst/NICMOS H-band (F160W) imaging data. Their inferred host light is $20.14\pm0.30$ mag in Vega system, which is also consistent to our inference ($20.00\pm0.15$ mag in Vega).}
%zeropoint 25.9463(AB) - 24.6949(Vega) = 1.2514
%HE1104 mag:  21.25 (AB)  --> 20.00 (Vega)

@@

\begin{figure*}
\centering
\begin{tabular}{c c}
\subfloat[HE0435]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/HE0435_inference.png}}&
\subfloat[RXJ1131]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/RXJ1131_inference.png}}\\
\subfloat[WFI2033]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/WFI2033_inference.png}}&
\subfloat[SDSS1206]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/SDSS1206_inference.png}}\\
\subfloat[HE1104]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/HE1104_inference.png}}&
\subfloat[SDSS0246]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/SDSS0246_inference.png}}\\
\subfloat[HS2209]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/HS2209_inference.png}}&
\subfloat[HE0047]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/HE0047_inference.png}}\\
\end{tabular}
\caption{\label{fig:image_inference} 
Illustrations of the inference using the best-fit lens model for each system using the AGN center noise level boosted approach. For each figure, the panels from left to right are the follows: Top row: (left to right): (1) observed data, (2) best-fit model (3) residuals divided by the uncertainty level. \pink{Some of the residual looks clumpy; however, they do not affect the host property measurements, for more details see Section~\ref{sec:diss}} ; Bottom row: (left to right): (4) data minus the model PSF and deflector  (i.e., pure lensed arc image), (5) the model of the lensed arc, (6) reconstructed host galaxy in the source plane with caustic line drawn as yellow line. Across all the systems, the lensed arc \pink{feature} can be clearly seen in the \pink{fourth} panel, indicating strong evidence of a detection. In panel (3) and (4), we use white regions to indicate the area where the noise level is boosted. 
}
\end{figure*}
